---
title: Referrals Analysis
authors:
- Emma Ideal
- Pat Caputo
- Josh Sacco
tags:
- recruiting
- referrals
created_at: 2017-02-15
updated_at: 2017-02-15
tldr: Investigating performance, application creation to offer extend times, and funnel success rates for SWE experienced referrals and non-referrals.
---

**Contents**

[TOC]

_NOTE: this will include a table of contents when rendered on the site._


### Goals

Inform recruiting strategy for SWE experienced candidates. Clients are Lori, EQ, Miranda, Jay, Nadir.

### Descriptives

```{r, echo=FALSE, warnings=FALSE}
library(ggplot2)
library(plyr)
```

This plot shows the number of unique lead candidates, referrals, and solicits in 2015, 2016, and YTD.

```{r, echo=FALSE}
# Read in the Hive data
r <- read.csv('/Users/eaideal/Desktop/Analysis/Referrals Analysis/SWE_Experienced/rec_hive2.csv', colClasses='character')[,c(1:4,7,10:11,20,25)]
names(r) <- c('ref_emp_id','fbid', 'candid', 'refid', 'pos', 'ques', 'reftype', 'dept', 'date_created')

# Clean date
r$date_created <- as.Date(format(as.Date(r$date_created, format="%Y-%m-%d"), "%Y-%m-%d"))
r$ref_yr <- as.character(format(r$date_created,'%Y'))

# Determine if the referral question contains the phrase "can vouch" or "worked vouch"
match <- c('can_vouch', 'worked_vouch')
r$vouch <- grepl(paste(match, collapse="|"), r$ques)

# Unique candidates referred by year and by type (for referrals within the Software Engineering departments)
d <- ddply(r[r$ref_yr %in% c(2015,2016,2017) & grepl('Software Engineering', r$dept),], .(reftype, ref_yr), summarise, n_cands = length(unique(candid)))

# Plot number of unique referred candidates by year and by referral type
ggplot(d, aes(reftype, n_cands)) +   
  geom_bar(aes(fill = ref_yr), position = "dodge", stat="identity") + 
  xlab('Referral Type') + ylab('Number of unique referred candidates') +
  theme(text = element_text(size=14)) + scale_y_continuous(breaks=seq(0,50000,by=2000))+
  ggtitle("All SWE Referrals") +
  theme(plot.title = element_text(hjust = 0.5))
```


### Referral Definitions

A referral is categorized into three groups:

- Strong referral - of "referral" type, which is determined by FB's referral tool + the referrer explicitly vouches for the candidate's professional competency
- Weak referral - any lead, solicit, or referral that is *not* a strong referral
- No referral - any lead, solicit, or referral that was submitted more than 50 days after their app is created or more than 365 days before their app is created

To define a referred *candidate*, my definitions are the following:

- Strongly referred - the candidate received only strong referrals
- Weak candidate - the candidate is not strongly referred but received at least one weak referral
- Never referred - either never referred through the referral tool, or referrals sent through the tool for this candidate fell outside the time band of interest

I then allow a candidate to fall in one of the above buckets for *each year* (2015, 2016, 2017 YTD).


### Key Takeaways

- Experienced SWE candidates that are hired through referrals perform better in their second PSC cycle ()
- Their app creation to offer extend times take stat. sig. fewer days compared to non-referrals (median diff ~ 1 week)
- Referred candidates get offers at a significantly higher rate (~8% compared to 3% for non-referrals), with strictly referred candidates receiving offers at a slightly higher rate than weakly referred
- Referrers with more seniority refer higher performing candidates

### Follow-ups

- All Tech
- All FB
- Promotion rates
